Title of Note Template ElegantNote \\[20pt] \Large Subtitle of notes

### 2023-04-14 book-en/book-cover-en.tex
update

% caption setting
\usepackage{caption}
%\captionsetup{font={small,singlespacing},labelformat={default},labelsep=period}
\captionsetup[figure]{position=bottom,skip={5pt},name={Figure}}
\captionsetup[table]{position=top,skip={2pt},name={Table}}
%\setlength{\textfloatsep}{12pt plus 2pt minus 2pt}
%\setlength{\floatsep}{10pt plus 2pt minus 2pt}
%\setlength{\intextsep}{10pt plus 2pt minus 2pt}
%\setlength{\abovecaptionskip}{2pt plus 1pt minus 1pt}
%\setlength{\belowcaptionskip}{3pt plus 1pt minus 2pt}

@@

% define new command
\newcommand{\CC}{\ensuremath{\mathbb{C}}}
\newcommand{\RR}{\ensuremath{\mathbb{R}}}
% new command
\newcommand{\abs}[1]{\lvert#1\rvert}
\newcommand{\norm}[1]{\lVert#1\rVert}
\newcommand{\dif}{\mathop{}\!\mathrm{d}}
\newcommand{\dx}[1][x]{\mathop{}\!\mathrm{d}#1}
\newcommand{\ii}{\mathrm{i}\mkern1mu} % imaginary
\newcommand{\refe}[2]{(\ref{#1})--(\ref{#2})}
\newcommand{\red}[1]{\textcolor{red}{#1}}

@@

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

@@

	\vspace{2\baselineskip} % Whitespace after the title block

	%------------------------------------------------
	%	Subtitle
	%------------------------------------------------

	% A Number of Fascinating and Life-changing Templates Presented in a Clear and Concise Way

	\vspace*{3\baselineskip} % Whitespace under the subtitle

@@

@@

we present a new method for solving the model equation
\begin{equation}\label{eq:mulequ}
\left\{\begin{aligned}
  & \partial_{t} u-\varepsilon^{2} \Delta u+u^{3}-u=0, \quad \text{ in } ~\Omega\times\mathcal{T}, \\
  &\, u(x,y,t) = g(t), \quad \text{ on } ~ \partial \Omega, \\
  &\, u(x,y,0)=\varphi(x, y), \quad \text{ on } ~\Omega.
\end{aligned}\right.
\end{equation}
where $\varepsilon$ is a small parameter.

@@

Figure \ref{fig:a} shows some example results.
\begin{figure}[htp!]
  \centering
  \includegraphics[width=0.48\linewidth]{image1}
  \caption{Example figure using external image files.}
  \label{fig:a}
\end{figure}

\clearpage
The two figures are placed side by side, sharing the same title.
\begin{figure}[htp!]
  \centering
  \includegraphics[width=0.45\linewidth]{image1}
  \hfill
  \includegraphics[width=0.45\linewidth]{image2}
  \caption{Left: Caption 1, Right: Caption 2.}
  \label{fig:b}
\end{figure}

Use \texttt{minipage} package to set up images side-by-side, each with its own title.
\begin{figure}[htp!]
\begin{minipage}[t]{0.48\linewidth}
  \centering
  \includegraphics[width=0.96\linewidth]{image1}
  \caption{Caption A}
  \label{fig:image1}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\linewidth}
\centering
   \includegraphics[width=0.95\linewidth]{image2}
   \caption{Caption B}
   \label{fig:image2}
\end{minipage}
\end{figure}

@@

This is Figure \ref{fig:aa}.
\begin{figure}[htp!]
  \centering
  \includegraphics[width=0.48\linewidth]{image1}
  \caption{Example figure using external image files.}
  \label{fig:aa}
\end{figure}

>>>>

% caption setting
\usepackage{caption}
%\captionsetup{font={small,singlespacing},labelformat={default},labelsep=period}
\captionsetup[figure]{position=bottom,skip={8pt},name={Figure}}
\captionsetup[table]{position=top,skip={4pt},name={Table}}
%\setlength{\textfloatsep}{12pt plus 2pt minus 2pt}
%\setlength{\floatsep}{10pt plus 2pt minus 2pt}
%\setlength{\intextsep}{10pt plus 2pt minus 2pt}
%\setlength{\abovecaptionskip}{2pt plus 1pt minus 1pt}
%\setlength{\belowcaptionskip}{3pt plus 1pt minus 2pt}

@@

% differential operator
\newcommand{\dif}{\mathop{}\!\mathrm{d}}

% new command
\newcommand{\CC}{\ensuremath{\mathbb{C}}}
\newcommand{\RR}{\ensuremath{\mathbb{R}}}
\newcommand{\abs}[1]{\lvert#1\rvert}
\newcommand{\norm}[1]{\lVert#1\rVert}
\newcommand{\dx}[1][x]{\mathop{}\!\mathrm{d}#1}
\newcommand{\ii}{\mathrm{i}\mkern1mu} % imaginary
\newcommand{\refe}[2]{(\ref{#1})--(\ref{#2})}
\newcommand{\red}[1]{\textcolor{red}{#1}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% TITLE PAGE

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

	\vspace{5\baselineskip} % Whitespace after the title block

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

we present a new method for solving the model equation
\begin{equation}\label{eq:mulequ}
\left\{\begin{aligned}
  & \partial_{t} u-\varepsilon^{2} \Delta u+u^{3}-u=0, \quad \text{in} ~\Omega\times\mathcal{T}, \\
  &\, u(x,y,t) = g(t), \quad \text{on} ~ \partial \Omega, \\
  &\, u(x,y,0)=\varphi(x, y), \quad \text{on} ~\Omega.
\end{aligned}\right.
\end{equation}
where $\varepsilon$ is a small parameter.

@@

Figure \ref{fig:sinx} shows some example results.
\begin{figure}[htp!]
  \centering
  \includegraphics[width=0.48\linewidth]{image1}
  \caption{Example figure using external image files.}
  \label{fig:sinx}
\end{figure}

\clearpage
The two figures are placed side by side, sharing the one title, as shown in Figure~\ref{fig:twofigs}.
\begin{figure}[htp!]
  \centering
  \includegraphics[width=0.45\linewidth]{image1}
  \hfill
  \includegraphics[width=0.45\linewidth]{image2}
  \caption{Left: Caption 1, ~ Right: Caption 2.}
  \label{fig:twofigs}
\end{figure}

Use \texttt{minipage} package to set images side-by-side, each with its own title, as shown in Figure~\ref{fig:A} and Figure~\ref{fig:B}.
\begin{figure}[htp!]
\begin{minipage}[t]{0.48\linewidth}
  \centering
  \includegraphics[width=0.96\linewidth]{image1}
  \caption{Caption A}
  \label{fig:A}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\linewidth}
\centering
   \includegraphics[width=0.95\linewidth]{image2}
   \caption{Caption B}
   \label{fig:B}
\end{minipage}
\end{figure}

@@

This is Figure~\ref{fig:sinx2}.
\begin{figure}[htp!]
  \centering
  \includegraphics[width=0.48\linewidth]{image1}
  \caption{Example figure using external image files.}
  \label{fig:sinx2}
\end{figure}

### 2023-04-14 note-temp/main-en.tex
update

@@

@@

%\bibliographystyle{thuthesis-numeric}
\bibliographystyle{plain}

@@

%\title{\LaTeX note template}
%\author{Author}
%\institute{}
%\version{1.3}
%\date{\zhtoday}
%\date{}

\begin{document}
%\maketitle

\input{cover2.tex}

@@

\section{code highlight}

@@

\begin{lstlisting}[style=matlab,title={MATLAB code}]
% Euler method for the ODE model
% u'(x)=x^2+x-u, x in [0,1]
% Initial condition: u(0)=0 ;
% Exact solution: u(x)=-exp(-x)+x^2-x+1.
clear all;  clf
h=0.1;
x=0:h:1;
N=length(x)-1;
u(1)=0;                        % initial value
fun=@(t,u) t.^2+t-u;           % RHS

for n=1:N
    u(n+1)=u(n)+h.*fun(x(n),u(n));
end

ue=-exp(-x)+x.^2-x+1;          % exact solution
plot(x,ue,'b-',x,u,'r+','LineWidth',1)
legend('Exact','Numerical','location','North')
%title('Euler method','fontsize',12)
set(gca,'fontsize',12)
xlabel('x','fontsize',16), ylabel('u','fontsize',16,'Rotation',0)
\end{lstlisting}

>>>>

%----- header and footer -----
\fancypagestyle{plain}{%
	\fancyhf{}
	\fancyhead[C]{\color{ecolor}\nouppercase{\leftmark}}
	\fancyfoot[C]{\color{gray}\thepage}
    \renewcommand{\headrulewidth}{0.5pt}
}

\pagestyle{plain}

@@

%----- maketitle -----
\makeatletter
\renewcommand*{\maketitle}{
\begin{titlepage}
    \pdfbookmark[1]{Cover}{cover}
    \centering
    %\scshape
    \vspace*{5\baselineskip}
    \color{ecolor}

    %-------- title ---------
    \rule{\textwidth}{1.6pt}\vspace*{-\baselineskip}\vspace*{2pt}
    \rule{\textwidth}{0.4pt}

    \vspace{0.75\baselineskip}

    {\LARGE\bfseries \@title}

	\vspace{0.75\baselineskip}

	\rule{\textwidth}{0.4pt}\vspace*{-\baselineskip}\vspace{3.2pt}
	\rule{\textwidth}{1.6pt}

	\vspace{4\baselineskip}

    %----- Author -----
    {\Large \@author}

    \vspace{0.35\baselineskip}

    {\Large \@date}
	\vfill
\end{titlepage}
\thispagestyle{empty}
}
\makeatother

@@

% bibliography style
%\bibliographystyle{thuthesis-numeric}
\bibliographystyle{plain}

@@

\title{Title of Note Template ElegantNote \\[20pt]
\Large Subtitle of notes
}
\author{Author}
%\institute{}
%\version{1.3}
%\date{\zhtoday}
\date{June, 2022}

\begin{document}

\maketitle

@@

\section{Code highlight}

@@

\begin{lstlisting}[style=matlab,title={MATLAB code}]
% Euler method for the ODE model
% u'(x)=x^2+x-u, x in [0,1]
% Initial condition: u(0)=0 ;
clear all;  clf
h=0.1;
x=0:h:1;
N=length(x)-1;
u(1)=0;                        % initial value
fun=@(t,u) t.^2+t-u;           % RHS
for n=1:N
    u(n+1)=u(n)+h.*fun(x(n),u(n));
end
ue=-exp(-x)+x.^2-x+1;          % exact solution
plot(x,ue,'b-',x,u,'r+','LineWidth',1)
legend('Exact','Numerical','location','North')
set(gca,'fontsize',12)
xlabel('x','fontsize',16), ylabel('u','fontsize',16)
\end{lstlisting}
